Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-10 acknowledgments.tex
updated acknowledgments to include grants and fix many tragic and hilarious typos.

This work has been supported by the National Science Foundation by
grants
AAG-0808184 (DRR),
AAG-1109008 (DRR),
ACI-9619019 (MLN),
ASC-9313135 (MLN),
AST-9803137 (MLN), 
AST-0307690 (MLN), 
AST-0407176 (RC),
AST-0407368 (SS, EJH),
AST-0507521 (RC) 
AST-0507717 (MLN), 
AST-0507768 (AK),
AST-0607675 (AK)
AST-0702923 (EJH),
AST-0707474 (BDS), 
AST-0708960 (MLN), 
AST-0807215 (JB),
AST-0808184 (MLN, AK),
AST-0908819 (BWO) 
AST-0955300 (NJG),
AST-1008134 (GB) 
AST-1009802 (JSO), 
AST-1102943 (MLN)
AST-1106437 (JB),
AST-1210890 (GB),
AST-1211626 (JW),
OCI-0832662 (BWO, MLN),
OCI-0941373 (BWO),
PHY-1104819 (MLN, JB),
the CI TraCS fellowship (OCI-1048505; MJT),
and the Graduate Research Fellowship program (NJG; SJS).

This work has been supported by the National Aeronautics and Space
Administration through grants
NAGW-3152 (MLN),
NAG5-3923 (MLN),
NNX08AH26G (MLN),
NNX09AD80G (BWO),
NNX12AH41G (GB),
NNX12AC98G (BWO),
NNZ07-AG77G (BDS),
NNG05GK10G (RC),
ATP09-0094 (SVL),
Chandra Theory grant \#TM9-0008X (BWO),
Hubble Space Telescope Theory Grant HST-AR-10978.01 (BDS),
the Fermi Guest Investigator Program (\#21077; BWO),
and the Hubble Postdoctoral Fellowship through the Space Telescope Science
Insititue, \#120-6370 (JW).

This work has been supported by the Department of Energy via the
Los Alamos National Laboratory (LANL) Laboratory Directed Research and
Development Program (BWO, DCC, HX, SJS), 
the LANL Institute for Geophysics and Planetary Physics (BWO, DCC, CP,
BC),
the Los Alamos National Laboratory Director's Postdoctoral Fellowship
program (No. DE-AC52-06NA25396;
BWO and DCC), and the
DOE Computational Science Graduate Fellowship (DE-FG02-97ER25308; SJS)

@@

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Tech,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

>>>>

This work has been supported by the National Science Foundation by
grants
AAG-0808184 (DRR),
AAG-1109008 (DRR),
ACI-9619019 (MLN),
ASC-9313135 (MLN),
AST-9803137 (MLN), 
AST-0307690 (MLN), 
AST-0407176 (RC),
AST-0407368 (SS, EJH),
AST-0507521 (RC) 
AST-0507717 (MLN), 
AST-0507768 (AK),
AST-0529734 (TA),
AST-0607675 (AK),
AST-0702923 (EJH),
AST-0707474 (BDS), 
AST-0708960 (MLN), 
AST-0807075 (TA),
AST-0807215 (JB),
AST-0808184 (MLN, AK),
AST-0808398 (TA),
AST-0908819 (BWO) 
AST-0955300 (NJG),
AST-1008134 (GB) 
AST-1009802 (JSO), 
AST-1102943 (MLN)
AST-1106437 (JB),
AST-1210890 (GB),
AST-1211626 (JHW),
OCI-0832662 (BWO, MLN),
OCI-0941373 (BWO),
PHY-1104819 (MLN, JB),
the CI TraCS fellowship (OCI-1048505; MJT),
and the Graduate Research Fellowship program (NJG; SWS).

This work has been supported by the National Aeronautics and Space
Administration through grants
NAGW-3152 (MLN),
NAG5-3923 (MLN),
NNX08AH26G (MLN, TA),
NNX09AD80G (BWO),
NNX12AH41G (GB),
NNX12AC98G (BWO),
NNZ07-AG77G (BDS),
NNG05GK10G (RC),
ATP09-0094 (SVL),
Chandra Theory grant \#TM9-0008X (BWO),
Hubble Space Telescope Theory Grant HST-AR-10978.01 (BDS),
the Fermi Guest Investigator Program (\#21077; BWO),
and the Hubble Postdoctoral Fellowship through the Space Telescope Science
Insititue, \#120-6370 (JHW).

This work has been supported by the Department of Energy via the
Los Alamos National Laboratory (LANL) Laboratory Directed Research and
Development Program (BWO, DCC, HX, SWS), 
the LANL Institute for Geophysics and Planetary Physics (BWO, DCC, CP,
BC),
the Los Alamos National Laboratory Director's Postdoctoral Fellowship
program (No. DE-AC52-06NA25396;
BWO and DCC), and the
DOE Computational Science Graduate Fellowship (DE-FG02-97ER25308; SWS)

@@

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Institute of Technology,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Southern Methodist University,
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Colorado at Boulder,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.
